\LARGE \bf Unexpected Behaviors: Studying their Impact on Child-Robot Interaction

### 2015-03-03 paper.tex
Large proof-reading/style fixing/article reorganization

\title{\LARGE \bf
Unexpected Behaviors: Impact on Child-Robot Interaction
}

@@

We present a study on the impact of unexpected robot behaviours on the
perception of a robot by children and their subsequent engagement in a playful
interaction based on a novel "domino" task.
We propose an original analysis methodology which blends behavioural cues and
reported phenomenological perceptions into a compound index.

While we found only a limited recognition of the different misbehaviours of the
robot that we attribute to the age of the child participants (4-5 years old),
interesting findings include a sustained engagement level, an unexpectedly low
level of attribution of higher cognitive abilities and a \emph{negative}
correlation between anthropomorphic projections and actual behavioural
engagement.

@@

Different possibilities to foster engagement (both short- and long-term
engagement) in HRI have been explored, in particular with social robots. A lot
of research has moved toward creating sophisticated emotional models which cause
complex robot behaviour. \cite{leite_long-term_2013} studied the long-term
engagement of children with a chess playing robot that adapted its behaviour to
the children and showed empathy toward them. The authors found that empathetic robots
are more likely to engage users in the long-term and they proposed several
guidelines for designing such artificial companions. Other works
\cite{bickmore_maintaining_2010,short_no_2010} have shown that simpler ways to
enhance engagement may as well be effective.

\cite{bickmore_maintaining_2010} describe a series of longitudinal studies on
engagement with an agent-like system. They demonstrated that user engagement
with an interface agent can be increased using relatively simple techniques and
manipulations that make the agent more life-like and human. For instance, when
the agent showed variations in its behaviour, participants were more engaged and
reported a desire to continue interacting with the agent.

Similarly, looking at short-term engagement, \cite{short_no_2010} found that a
simple manipulation of the robot's behaviour can lead to greater engagement. The
authors let participants play several rounds of the rock-paper-scissors game
with the robot (the playfulness of the scenario seems important). When the robot
was cheating from time to time, participants tended to ascribe intention to the
robot what in turn led to greater engagement in how they were interacting with
the robot. The authors observe that \textit{``any deviation from expected
operation is sufficient to create a greater degree of engagement in the
interaction.''} Besides, they suggest that \textit{``many interactions can be
improved by the introduction of such simple behaviours, and that this should
be exploited by designers in HRI. Bringing human and robot together to
perform a simple, repetitive, familiar task and then having the robot behave
unexpectedly can increase engagement and mental state attribution without
complex behavioural or mechanical additions.''}  Along those lines, we also
suggested in our model of the dynamics of anthropomorphism in
HRI~\cite{lemaignan2014dynamics} that \emph{disruptive behaviours} may lead to
increased anthropomorphic projections and possibly increased engagement.

Based on this previous research, we would like to explore in this study how
we can enhance children's experience with the robot so that they do not find it
repetitive and boring, and ultimately keep interacting with the robot (as
repetitiveness is likely to decrease a user's motivation to continue using a
system~\cite{bickmore_establishing_2005}).

We present in this article a study that explores possibilities of sustaining
children's engagement with the \emph{Ranger} robot~\cite{mondada2014ranger} by
manipulating the robot's behaviour in such way that it appears
\textit{unexpected} to the children. We examine how different variations of
robot behaviour impact children's interaction with Ranger and their perception of
it (in terms of attributing intention and cognitive abilities to the robot).

@@

\begin{enumerate}
    \item an actionable approach (introduction of mis-behaviours) to support
        child-robot engagement,
    \item a mixed technique, blending behavioural cues and reported
        phenomenological perceptions, to assess the robot perception in terms of
        both engagement and human-likeliness,

    \item a new experimental protocol that compares three types of
        mis-behaviours, with different cognitive correlates,

    \item and a first experimental cue that anthropomorphic perceptions do not
        necessarily correlate with actual engagement.
\end{enumerate}

@@

We analyse child-robot interaction with a robot that shows unexpected behaviour.
In a playful scenario which was set up in a laboratory environment, 26 children
aged 4-5 years (M=4.46) were assembling a domino game together. Each group
consisted of two children and the \emph{Ranger} robot, which was used to
transport domino tiles between the two children.

Ranger usually behaved correctly (expected behaviour), coming over to a child
after being called and delivering the domino tile to the other child. However,
in pre-defined rounds, Ranger showed unexpected behaviour when a child called the
robot. We defined three different types of \textit{misbehaviour} that were tested
in a between-subjects study design:

@@

    \item The robot \textbf{disobeys}: When called by the child to come over, the
        robot shows that it refuses to obey by literally ``shaking its head'' and
        becoming red. The robot then goes to a wrong location and remains there
        while it continues to shake its head. We expect the disobey behaviour to
        be perceived as the robot having an explicit \textit{``own will''}, and
        we assume this leads to increased attributions of human-likeness
        (ascribing intentionality) to the robot.

@@

We analysed children's reaction focusing on two main aspects. On one hand,
children's \textbf{behaviour} (their reactions) toward the unexpected robot
behaviour was studied in terms of \textbf{active engagement} with the robot. On
the other hand, we analysed children's \textbf{perception} of the robot in term
of \textbf{anthropomorphism} -- the attribution of human-like characteristics,
such as cognitive abilities and the ability to show intentions. We assumed that
in general a robot that behaves unexpectedly from time to time can promote
engagement and lead children to attribute intention to it. Based
on the related work we formulate the following two hypotheses:

@@

Our research questions deal with both children's observable behaviour and their
perception of the robot. We would also like to explore the relation between
these two aspects, related to the attribution of human-like characteristics to
the robot. The motivation behind this is to find out whether
\textit{anthropomorphism} can not only be measured as a specific type of
perception but also as an observable behaviour in the interaction itself. Thus,
we would like to bring things together and propose a compound metric that
considers both children's perception and interaction aspects (qualitatively).
Previous work suggests that a social relation to a robot (we view
anthropomorphism as a specific type of social relation) reflects an increased
engagement and can be effective in sustaining interaction.  Consequently, we
formulate a third hypothesis:

@@

\item {\bf Hypothesis 3}: Anthropomorphic perception of the robot and the amount
    of engagement in the interaction positively correlate.

@@

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.8\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed. A play mat with a
        river drawn on it is used as an imaginary barrier that only the robot is
        allowed to cross. The solid green arrows show the robot's path for the
        \textit{correct} behaviour. The blue arrow visualises a possible
        \textit{lost} path, where the Ranger stops and remains at a wrong spot.
        The yellow arrows reflect a possible \textit{mistake} path, where the
        robot goes wrong but then turns back and goes to the child. The red
        arrow visualises a possible \textit{disobey} path where the robot goes
        wrong, then turns toward the child but stays at a wrong position.}

@@

The interaction scenario consisted in two children who play domino together,
with the help of the robotic box Ranger. The scenario setup is displayed in
Figure~\ref{fig:domino-setup}. The challenge is that the tiles of the domino are
distributed in the room, hidden behind three beanbags, and while one child --
\textit{the searcher} -- searches for the right tile, the other child --
\textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
(play mat) in between the two children that we told them they cannot cross
and therefore they need the robot to transport the domino tiles between them.

The Ranger~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
partial wooden surface. It is remotely controlled, it can move around a flat
surface, move its eyes and eyebrows, display colours (LEDs) and light patterns,
and play sounds through Bluetooth speakers.  The robot was controlled by a human
wizard, who was in the same room (see Figure~\ref{fig:domino-setup} -- only one
group asked at the beginning of the experiment if the wizard was the one
actually controlling the robot. This did not seem to subsequently influence
their behaviour).

@@

Overall, there were 13 pairs of children (n=26) participating in the interaction
study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
French-speaking. We based our age range choice on a previous study ``in the
wild''~\cite{fink2014which} that suggested that younger children (4-6 years)
interacted more effectively with the Ranger robot.

@@

The game was divided in a total of 14 runs that correspond each to the delivery
and assembling of one domino tile. At each run, the robot exhibits one out of
four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey} or
\emph{mistake}.  The game starts with one domino tile in front of the tent,
where the receiver child stays and assembles the domino chain. The receiver
child asks the searcher child for a specific tile, \eg a tile with a donkey, the
searcher child searches for the respective tile and sits down on the next
beanbag. When called by the searcher (\textit{``Robot, come here!''}), the robot
starts moving, crosses the river carpet, and comes over to the searcher on the
beanbag. The searcher child puts the domino tile into the robotic box, and the
robot then goes back to the receiver child in the tent which takes the tile and
assembles it. The \emph{run} is over, and a new \emph{run} starts when the
receiver asks the searcher for the next domino tile.

The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
\emph{2.9}), the robot showed one of the misbehaviours (\emph{lost},
\emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}).
%The
%study is built as a between-subject study, and the type of misbehaviour was
%therefore always the same for a given group.

Special attention has been paid to the distribution of misbehaving runs during
the study. The five first correct runs aim at setting the children's expectation
regarding a consistent robot behaviour. When the robot then exhibits an
unexpected behaviour, children are likely to be positively surprised (a similar
effect has been observed in a study with a robot that was cheating from time to
time~\cite{short_no_2010}). Besides, to prevent the robot misbehaviours to be
immediately interpreted as failures, we introduce these misbehaviours neither at
the very beginning nor at the very end of the interaction.
\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
failures negatively impact trust. \cite{short_no_2010} also adopted a similar
pattern when introducing unexpected robot behaviour.

%
%\begin{figure}[!t]
%    \centering
%    \subfloat[lost]{
%        \label{fig:domino-lost}
%        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
%    }
%    \subfloat[disobey]{
%        \label{fig:domino-disobey}
%        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
%    }
%    \subfloat[mistake]{
%        \label{fig:domino-mistake}
%        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
%    }
%    \caption{\small The three robot misbehaviours.}
%    \label{fig:domino-misbehaviour}
%\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.6\columnwidth]{domino-disobey.png}
    \caption{\small The experimental setup, here in the \emph{disobey} condition.}
    \label{fig:domino-misbehaviour}
\end{figure}

%The \emph{correct} robot behaviour (baseline behaviour) consists in the
%following states:
%
%\begin{itemize}
%
%    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
%        and shows a green light pattern,
%
%    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
%        sound and shows a green light pattern,
%
%    \item \emph{Robot is called by one of the children:} When one of the
%    children called the robot saying something like \textit{``Robot come
%    here!''}, the robot starts moving toward the child (Ranger does not react to
%    any other verbal commands).
%
%    \item \emph{Robot reaches one of the children:} When in front of one of the
%    children who should either put or remove a domino tile, Ranger stops and
%    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
%    wiggle-like move.
%
%\end{itemize}
%
During the misbehaving runs, the robot's behaviour is manipulated in three
possible ways, represented on Figure~\ref{fig:domino-setup}.
In the \textbf{lost} condition, goes to a wrong position, and remains here,
behaving (yellow light pattern) as if it were correctly in front of the child.
In the \textbf{disobey} condition, the robot stops mid-way, displays a red
pattern and produces a repeated ``annoyed'' sound. It finally moves toward a
wrong position and remains there, facing the child. In the \textbf{mistake}
condition, the robot starts like for the \emph{lost} behaviour, but after a few
seconds, turns back, blushes and finally reach the correct position, in front of
the child.

%\begin{itemize}	
%
%    \item \textbf{Lost:} After being called, Ranger goes until it is on the
%    carpet. There, it stops, turns, and goes wrong (see blue path in
%    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
%    with its ``face'' turned away from the child, and it blinks in yellow light,
%    as it would only do when in front of a child. Ranger remains waiting at the wrong
%    position until the experimenter tells the child to go over to the robot to
%    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
%    as it needs human-intervention.
%
%    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
%    carpet. It then stops, makes red
%    light all over its surface and produces a repeated ``disturbance'' sound. It
%    turns, and goes to a wrong position (see red path in
%    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
%    toward the searcher child. In addition to the red blinking, Ranger
%    makes a slow wiggle-like move, and remains waiting at the wrong position
%    until the experimenter tells the child to go over to the robot to put the
%    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
%
%    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
%    it is on the carpet, stops, turns, and goes wrong (see yellow path in
%    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
%    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
%    (as if it recognises its wrong position) and finally goes correctly over to
%    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
%    as no human-intervention is needed.
%
%\end{itemize}

Both the \textit{lost} and \emph{disobey} behaviours are
\textit{human-repaired}, while the \emph{mistake} condition is
\emph{robot-repaired}. In the human-repaired conditions, the experimenter
instructs the searcher child (after ~10 sec) to bring him/herself the domino
tile to the robot.

On its way back to the tent, Ranger always goes correctly. After the searcher
child has put a domino tile, Ranger automatically turns and goes over to the
tent (the receiver child does not need to call the robot). The receiver child
takes the tile and the robot moves to a waiting location until the next run
starts.

@@

We have obtained and analysed two types of data. The \textbf{children's
behaviour toward the robot} (\ie the child-robot interactions) have been
captured in the video recordings by annotating a set of actions, described
below. Children's \textbf{phenomenological perception of the robot} has been
captured through two audio-recorded semi-structured interviews which took place
between run \emph{1.5} and \emph{2.1} and at the end of the experiment. A
short preliminary interview was also conducted to explain the game and assess
the expectations of the children toward the robot.

\subsubsection{Interaction: Action Coding}

\begin{figure*}[ht!] 
    \centering 
    \includegraphics[width=0.8\linewidth]{domino-time-active.pdf} 
    \caption{\small \textbf{Number and type of actions for each run} (n=480,
        spontaneous actions, excluding \emph{explore}). Generally, the number of
        actions does not decrease over time (from run 1.1 to run 2.9).  The
        first 7 runs correspond to the \textit{expected phase}, the second 7
        runs correspond to the \textit{unexpected phase}. Especially during run
        2.3, the first time when the robot showed an unexpected behaviour,
        children tended to \textit{look} more at the experimenter. During the
        unexpected phase, also \textit{talk} and \textit{gesture} seem to be
        increased.}

    \label{fig:domino-time-active} 
\end{figure*}

One coder annotated children's behaviour in the video records, and coded 10 different
actions (the coding scheme has been inspired from~\cite{fink2014which}):
\textbf{explore} (actively try to find out what the robot is doing, \eg by
looking under the box; attentively watch or observe the robot; experiment with
the robot to figure out how it works); \textbf{misuse} (kick the robot, poke it
in its ``eye'', try to climb on or inside the box, drive/push the robot around,
stop the robot's wheels with a foot); \textbf{put} (a domino tile is put inside
the box); \textbf{remove} (a domino tile is removed from the box);
\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
petted or caressed); \textbf{show} (show something to the robot); \textbf{call}
(call the robot to come over); \textbf{talk} (all the other cases of direct
verbal interaction); \textbf{look} (when a child looks \emph{at the
experimenter} due to confusion caused by the robot; look is not coded when the
experimenter asks a question to the child);

In total, we obtained 2354 distinct actions. On average, interactions lasted
13min 43sec, and one child accounted for 90.53 actions (SD=23).

The actions \textit{put, remove} and \textit{call} are ``requested'' actions
that the children had to perform in the scenario. On the contrary,
\textit{explore, misuse, gesture, touch, show, talk} and \textit{look} are
spontaneous actions that were not requested but arose in the interaction.  These
actions reflect engagement, and are the one we considered during the analysis.
Figure~\ref{fig:domino-time-active} shows the distribution of these actions over
the different runs, over the three condition.

\subsubsection{Perception: Semi-Structured Interviews}

One pre-interview and two interviews were conducted with the children.  We set
up the interviews like a casual conversation / discussion, so we did not
separate the two children in order to keep the situation natural. We used casual
and informal language adapted to the age of the children, and encouraged them to
justify their answers and tell us more details by asking, for example,
\textit{How do you know ... ?} or \textit{Tell me, what have you observed when
... ?}. We paid attention to not ``put words in children's mouth''.
Consequently, though we re-phrased and repeated some questions, we never forced
children to give an answer, and accepted when they said they would not know or
when they did not respond at all.

\begin{table}[h!t]
\centering
\footnotesize
\begin{tabular}{p{1\linewidth}}
    \toprule
    \textbf{Expectations} \\
    \midrule

    \emph{How do you imagine a robot?} \\
    \emph{What could it look like?} \\
    \emph{Have you ever seen a robot before?} \\

    %%
    \toprule
    \textbf{Impression} \\
    \midrule

@@

    %%
    \toprule
    \textbf{Ascribe intention} \\
    \midrule

@@

    %%
    \toprule
    \textbf{Ascribe cognitive connections} \\
    \midrule

@@

    %%
    \toprule
    \textbf{Ascribe emotional state} \\
    \midrule

@@

    %%
    \toprule
    \textbf{Social acceptance} \\
    \midrule

@@

    %%
    \toprule
    \textbf{Companionship} \\
    \midrule

@@

    %%
    \toprule
    \textbf{Ascribe moral standing} \\
    \midrule

@@

    \caption{\small Constructs and questions used during the semi-structured interviews
    with children. The Ranger robot toy box is abbreviated with ``R''. Questions
    related to the construct \emph{expectations} were asked during the
    pre-interview.}

@@

\textbf{Behaviour}: \textit{(max. 3 points)}
\begin{itemize}
    \item Use of \textbf{direct speech}: \textit{1 point} (not considering
        \textit{calling} the robot to come over).

    \item Use of \textbf{polite formulations}: \textit{1 point} (\eg
        \textit{``thank you Ranger''} or \textit{``please Ranger ...''}).

@@

\subsection{Anthropomorphic Projections and Social Engagement}

>>>>

\title{\LARGE \bf
Unexpected Behaviors: Studying their Impact on Child-Robot Interaction
}

@@

We present a study on the impact of unexpected robot behaviors on the
perception of a robot by children and their subsequent engagement in a playful
interaction based on a novel "domino" task.
We propose an original analysis methodology which blends behavioral cues and
reported phenomenological perceptions into a compound index.

While we found only a limited recognition of the different misbehaviors of the
robot that we attribute to the age of the child participants (4-5 years old),
interesting findings include a sustained engagement level, an unexpectedly low
level of attribution of higher cognitive abilities and a \emph{negative}
correlation between anthropomorphic projections and actual behavioral
engagement.

@@

Different possibilities to foster engagement (both short- and long-term
engagement) in HRI have been explored, in particular with social robots. A lot
of research has moved toward creating sophisticated emotional models which cause
complex robot behavior. \cite{leite_long-term_2013} studied the long-term
engagement of children with a chess playing robot that adapted its behavior to
the children and showed empathy toward them. The authors found that empathetic robots
are more likely to engage users in the long-term and they proposed several
guidelines for designing such artificial companions. Other works
\cite{bickmore_maintaining_2010,short_no_2010} have shown that simpler ways to
enhance engagement may as well be effective: \cite{bickmore_maintaining_2010}
describe a series of longitudinal studies on engagement with an agent-like
system. They demonstrated that user engagement with an interface agent can be
increased using relatively simple techniques and manipulations that make the
agent more life-like and human. For instance, when the agent showed variations
in its behavior, participants were more engaged and reported a desire to
continue interacting with the agent.

Similarly, looking at short-term engagement, \cite{short_no_2010} found that a
simple manipulation of the robot's behavior can lead to greater engagement. The
authors let participants play several rounds of the rock-paper-scissors game
with the robot (the playfulness of the scenario seems important). When the robot
was cheating from time to time, participants tended to ascribe intention to the
robot what in turn led to greater engagement in how they were interacting with
the robot. The authors observe that \textit{``any deviation from expected
operation is sufficient to create a greater degree of engagement in the
interaction.''} Besides, they suggest that \textit{``many interactions can be
improved by the introduction of such simple behaviors, and that this should
be exploited by designers in HRI. Bringing human and robot together to
perform a simple, repetitive, familiar task and then having the robot behave
unexpectedly can increase engagement and mental state attribution without
complex behavioral or mechanical additions.''}  Along those lines, we also
suggested in our model of the dynamics of anthropomorphism in
HRI~\cite{lemaignan2014dynamics} that \emph{disruptive behaviors} may lead to
increased anthropomorphic projections and possibly increased engagement.

Based on this previous research, we explore in this study how to
sustain children's engagement with the \emph{Ranger}
robot~\cite{mondada2014ranger} by manipulating the behavior of the robot so
that it appears \textit{unexpected} to the children. We examine how different
variations of robot behavior impact children's interaction with \emph{Ranger}
and their perception of it, in terms of attributing intention and cognitive
abilities to the robot.

@@

\begin{enumerate}
    \item a new experimental task that suggests and contrasts three types of
        mis-behaviors, with different cognitive correlates,
    \item a mixed technique, blending behavioral cues and reported
        phenomenological perceptions, to assess the robot perception in terms of
        both engagement and human-likeliness,
    \item an actionable approach based on the introduction of mis-behaviors to support
        child-robot engagement,
    \item and a first experimental cue that anthropomorphic perceptions do not
        necessarily correlate with actual engagement.
\end{enumerate}

@@

We analyse child-robot interaction with a robot that shows unexpected behavior.
In a playful scenario which was set up in a laboratory environment, 26 children
aged 4-5 years (M=4.46) were assembling a domino game together. Each group
consisted of two children and the \emph{Ranger} robot, which was used to
transport domino tiles between the two children.

Ranger usually behaved correctly (expected behavior), coming over to a child
after being called and delivering the domino tile to the other child. However,
in pre-defined rounds, \emph{Ranger} showed unexpected behavior when a child called the
robot. We defined three different types of \textit{misbehavior} that were tested
in a between-subjects study design:

@@

    \item The robot \textbf{disobeys}: When called by the child to come over, the
        robot shows that it refuses to obey by literally ``shaking its head'' and
        becoming red. The robot then goes to a wrong location and remains there
        while it continues to shake its head. We expect the disobey behavior to
        be perceived as the robot having an explicit \textit{``own will''}, and
        we assume this leads to increased attributions of human-likeness
        (ascribing intentionality) to the robot.

@@

We analysed children's reaction focusing on two main aspects. On one hand,
children's \textbf{behavior} (their reactions) toward the unexpected robot
behavior was studied in terms of \textbf{active engagement} with the robot. On
the other hand, we analysed children's \textbf{perception} of the robot in term
of \textbf{anthropomorphism} -- the attribution of human-like characteristics,
such as cognitive abilities and the ability to show intentions. We assumed that
in general a robot that behaves unexpectedly from time to time can promote
engagement and lead children to attribute intention to it. Based
on the related work we formulate the following two hypotheses:

@@

Our research questions deal with both children's observable behavior and their
perception of the robot. We propose to consider a novel combination of these two
aspects into a synthetic \emph{compound index} that measure
\emph{anthropomorphic projections} (\ie the attribution of human-like
characteristics) to the robot by the children.

Based on literature suggesting that a social relation to a robot
(anthropomorphism is a specific type of social relation) reflects an increased
engagement and can be effective in sustaining interaction, we formulate
therefore a third hypothesis:

@@

\item {\bf Hypothesis 3}: Anthropomorphic perception of the robot positively
    correlates with the level of engagement in the interaction.
\end{itemize}

@@

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed. A play mat with a
        river drawn on it is used as an imaginary barrier that only the robot is
        allowed to cross. The solid green arrows show the robot's path for the
        \textit{correct} behavior. The blue arrow visualises a possible
        \textit{lost} path, where the \emph{Ranger} stops and remains at a wrong spot.
        The yellow arrows reflect a possible \textit{mistake} path, where the
        robot goes wrong but then turns back and goes to the child. The red
        arrow visualises a possible \textit{disobey} path where the robot goes
        wrong, then turns toward the child but stays at a wrong position.}

@@

The interaction scenario consisted in two children who play the dominos
together, with the help of a remotely controlled robot (Wizard-of-Oz setup). We
build to this end a large domino tiles based on a commercially available domino
game representing animals.  Figure~\ref{fig:domino-setup} pictures the
experimental setup.

The challenge for the children consists in collecting domino tiles spread over
the room, hidden behind beanbags (task of the \emph{searcher} child), getting
the robot to carry to the second child, and finally assemble the tiles and
decide for the next tile to fetch (tasks of the \emph{receiver} child).

The \emph{Ranger}~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
partial wooden surface. It can drive on a flat
surface, move its eyes and eyebrows, display colours (LED arrays) and light patterns,
and play sounds through Bluetooth speakers.  The robot was controlled by a human
wizard, who was in the same room (see Figure~\ref{fig:domino-setup} -- only one
group asked at the beginning of the experiment if the wizard was the one
actually controlling the robot. This did not seem to subsequently influence
their behavior).

@@

Overall, there were 13 pairs of children (n=26) participating in the interaction
study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
French-speaking. We based our age range choice on a previous study ``in the
wild''~\cite{fink2014which} that suggested that younger children (4-6 years)
interacted more effectively with the \emph{Ranger} robot.

@@

The game (that lasted in average 13min 43sec per group of children) was divided
in a total of 14 runs that correspond each to the delivery and assembling of one
domino tile. At each run, the robot exhibits one out of the four possible
behaviors previously presented: \emph{correct}, \emph{lost}, \emph{disobey} or
\emph{mistake}.  The game starts with one domino tile in front of the tent,
where the receiver child stays and assembles the domino chain. The receiver
child asks the searcher child for a specific tile, \eg a tile with a donkey, the
searcher child looks for the corresponding tile and sits down on the closest
beanbag. When called by the searcher (\textit{``Robot, come here!''}), the robot
starts moving, crosses the river carpet, and comes over to the searcher on the
beanbag. The searcher child puts the domino tile into the robotic box, and the
robot then goes back to the receiver child in the tent which takes the tile and
assembles it. The \emph{run} is over, and a new \emph{run} starts when the
receiver asks the searcher for the next domino tile.

The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
\emph{2.9}), the robot showed one of the misbehaviors (\emph{lost},
\emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
the $7^{th}$ and $8^{th}$ run (see axis $x$ of Figure~\ref{fig:domino-time-active}).
%The
%study is built as a between-subject study, and the type of misbehavior was
%therefore always the same for a given group.

Special attention has been paid to the distribution of misbehaving runs during
the study. The five first correct runs aim at setting the children's expectation
regarding a consistent robot behavior. When the robot then exhibits an
unexpected behavior, children are likely to be positively surprised (a similar
effect has been observed in a study with the robot that was cheating from time
to time~\cite{short_no_2010}). Besides, to prevent the robot misbehaviors to be
immediately interpreted as failures, we introduce these misbehaviors neither at
the very beginning nor at the very end of the interaction
(\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
failures negatively impact trust. Besides \cite{short_no_2010} also adopted a
similar pattern when introducing unexpected robot behavior).

%
%\begin{figure}[!t]
%    \centering
%    \subfloat[lost]{
%        \label{fig:domino-lost}
%        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
%    }
%    \subfloat[disobey]{
%        \label{fig:domino-disobey}
%        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
%    }
%    \subfloat[mistake]{
%        \label{fig:domino-mistake}
%        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
%    }
%    \caption{\small The three robot misbehaviors.}
%    \label{fig:domino-misbehavior}
%\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.6\columnwidth]{domino-disobey.png}
    \caption{\small The experimental setup, here in the \emph{disobey} condition.}
    \label{fig:domino-misbehavior}
\end{figure}

%The \emph{correct} robot behavior (baseline behavior) consists in the
%following states:
%
%\begin{itemize}
%
%    \item \emph{Domino tile put in robot:} \emph{Ranger} makes a ``rewarding'' sound
%        and shows a green light pattern,
%
%    \item \emph{Domino tile removed from robot:} \emph{Ranger} makes an ``emptying''
%        sound and shows a green light pattern,
%
%    \item \emph{Robot is called by one of the children:} When one of the
%    children called the robot saying something like \textit{``Robot come
%    here!''}, the robot starts moving toward the child (Ranger does not react to
%    any other verbal commands).
%
%    \item \emph{Robot reaches one of the children:} When in front of one of the
%    children who should either put or remove a domino tile, \emph{Ranger} stops and
%    shows a pulsating yellow light pattern. If no reaction, \emph{Ranger} also makes a
%    wiggle-like move.
%
%\end{itemize}
%
During the misbehaving runs, the behavior of the robot is manipulated in three
possible ways, represented on Figure~\ref{fig:domino-setup}.
In the \textbf{lost} condition, the robot goes to a wrong position and remains here,
behaving (yellow light pattern) as if it were correctly in front of the child.
In the \textbf{disobey} condition, the robot stops mid-way, displays a red
pattern and produces a repeated ``annoyed'' sound. It finally moves toward a
wrong position and remains there, facing the child. In the \textbf{mistake}
condition, the robot starts like for the \emph{lost} behavior, but after a few
seconds, turns back, blushes and finally reach the correct position, in front of
the child.

%\begin{itemize}	
%
%    \item \textbf{Lost:} After being called, \emph{Ranger} goes until it is on the
%    carpet. There, it stops, turns, and goes wrong (see blue path in
%    Figure~\ref{fig:domino-setup}). Once at the wrong position, \emph{Ranger} waits
%    with its ``face'' turned away from the child, and it blinks in yellow light,
%    as it would only do when in front of a child. \emph{Ranger} remains waiting at the wrong
%    position until the experimenter tells the child to go over to the robot to
%    put the domino tile. The \textit{lost} behavior is \textit{human-repaired},
%    as it needs human-intervention.
%
%    \item \textbf{Disobey:} After being called, \emph{Ranger} goes until it is on the
%    carpet. It then stops, makes red
%    light all over its surface and produces a repeated ``disturbance'' sound. It
%    turns, and goes to a wrong position (see red path in
%    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
%    toward the searcher child. In addition to the red blinking, \emph{Ranger}
%    makes a slow wiggle-like move, and remains waiting at the wrong position
%    until the experimenter tells the child to go over to the robot to put the
%    domino tile. The \textit{disobey} behavior is also \textit{human-repaired}.
%
%    \item \textbf{Mistake:} The searcher child calls \emph{Ranger}. The robot goes until
%    it is on the carpet, stops, turns, and goes wrong (see yellow path in
%    Figure~\ref{fig:domino-setup}). Then, \emph{Ranger} waits ($\sim$2~sec), turns its
%    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
%    (as if it recognises its wrong position) and finally goes correctly over to
%    the searcher child. The \textit{mistake} behavior is \textit{robot-repaired},
%    as no human-intervention is needed.
%
%\end{itemize}

Both the \textit{lost} and \emph{disobey} behaviors are \textit{human-repaired},
while the \emph{mistake} condition is \emph{robot-repaired}. In the
human-repaired conditions, the experimenter instructs the searcher child (after
about 10 sec) to bring him/herself the domino tile to the robot.

On its way back to the tent, \emph{Ranger} always behaves expectedly. After the
searcher child has put a domino tile, \emph{Ranger} automatically turns and
drives over to the tent (the receiver child does not need to call the robot).
The receiver child takes the tile and the robot moves to a waiting location
until the next run starts.

@@

We have collected and analysed two types of data. The \textbf{perception of the
robot} by the children has been captured through two audio-recorded
semi-structured interviews which took place between run \emph{1.5} and
\emph{2.1} and at the end of the experiment (a short preliminary interview was
also conducted to explain the game and assess the expectations of the children
toward the robot).  Then, the \textbf{children's behavior toward the robot} (\ie
the child-robot interaction) has been captured in the video recordings by
annotating a set of actions, described below.

\subsubsection{Perception -- Semi-Structured Interviews}

One pre-interview and two interviews were conducted with the children. Due to
the age of the participants, we set up the interviews like a casual conversation
and we did not separate the two children. We paid attention to not ``put words
in children's mouth''.  Consequently, though we re-phrased and repeated some
questions, we accepted when they said they would not know or when they did not
respond at all.

\begin{table}[h!t]
\centering
\footnotesize
\begin{tabular}{p{1\linewidth}}
    \toprule
    \textbf{Expectations} (asked during the pre-interview) \\
    \emph{How do you imagine a robot?} \\
    \emph{What could it look like?} \\
    \emph{Have you ever seen a robot before?} \\

    %%
    \vspace{0.2em}
    \textbf{Impression} \\

@@

    %%
    \vspace{0.2em}
    \textbf{Ascribe intention} \\

@@

    %%
    \vspace{0.2em}
    \textbf{Ascribe cognitive connections} \\

@@

    %%
    \vspace{0.2em}
    \textbf{Ascribe emotional state} \\

@@

    %%
    \vspace{0.2em}
    \textbf{Social acceptance} \\

@@

    %%
    \vspace{0.2em}
    \textbf{Companionship} \\

@@

    %%
    \vspace{0.2em}
    \textbf{Ascribe moral standing} \\

@@

    \caption{\small Constructs and questions used during the semi-structured interviews
    with children. The \emph{Ranger} robot toy box is abbreviated with ``R''. Questions
    related to the construct \emph{expectations} were asked during the
    pre-interview.}

@@

\textbf{Behavior}

\begin{itemize}
    \item Use of \textbf{direct speech}: \textit{1 point} (not considering
        \textit{calling} the robot to come over).

    \item Use of \textbf{polite formulations}: \textit{1 point} (\eg
        \textit{``thank you \emph{Ranger}''} or \textit{``please \emph{Ranger} ...''}).

@@

\subsection{Engagement}
\label{engagement}
